Run the model

### 2019-12-09 scripts/3_model/2_run_model.Rmd
Added ticks to Fig2c and Fig 3 as required by the production team

```{r}
(delta_costs_plot <- ggplot(data = both) +
  geom_line(aes(
    x = R,
    y = rel_delta_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Costs avoided\nby trading") +
  scale_color_viridis_c(limits = c(0, 1)) +
  theme(
    text = element_text(size = 10),
    axis.text = element_text(size = 8)
  ) +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1),
                     limits = c(0.885, 1)) +
  theme(legend.position = "None"))
```

@@

```{r, fig.height = 3.5, fig.width = 5.5}
(allocation_cost_plot <- allocation %>%
   filter(R > 0,
          trade) %>% 
   mutate(trade = ifelse(trade, "Trading", "No Trading"),
          alpha = as.character(alpha)) %>% 
   group_by(trade, alpha, R, theta) %>%
   summarize(rev = sum(rev_tot)) %>%
   ungroup() %>%
   mutate(cost = (best_rev - rev) / best_rev) %>%
   ggplot(aes(x = R, y = cost, color = theta, group = paste(alpha, theta), linetype = alpha)) +
   geom_line(size = 1.5) +
   scale_y_continuous(labels = scales::percent,
                      limits = c(0, 1)) +
   xlab("Portion of patch as reserve (R)") +
   ylab("Losses\n(relative to R = 0)") +
   scale_color_viridis_c() +
   scale_linetype_manual(values = c("solid", "dashed", "dotted")) +
   ggtheme_plot() +
   guides(color = guide_colorbar(title = bquote("Movement ("~theta~")"),
                                 ticks.colour = "black",
                                 frame.colour = "black"),
          linetype = guide_legend(title = bquote("Allocation ("~alpha~")"),
                                  override.aes = list(size = 0.5))))
```

>>>>

```{r}
(delta_costs_plot <- ggplot(data = both) +
  geom_line(aes(
    x = R,
    y = rel_delta_cost,
    group = theta,
    color = theta
  ),
  size = 1
  ) +
  xlab("Portion of patch as reserve (R)") +
  ylab("Costs avoided\nby trading") +
  scale_color_viridis_c(limits = c(0, 1)) +
  theme(
    text = element_text(size = 10),
    axis.text = element_text(size = 8)
  ) +
  startR::ggtheme_plot() +
  scale_y_continuous(labels = scales::percent_format(accuracy = 0.1),
                     limits = c(0.885, 1)) +
  scale_x_continuous(limi= c(0, 1)) +
  theme(legend.position = "None"))

ggsave(plot = delta_costs_plot,
       filename = here("docs", "img", "panel2c.pdf"),
       width = 3.4, height = 2.3)
```

@@

```{r, fig.height = 3.5, fig.width = 5.5}
(allocation_cost_plot <- allocation %>%
   filter(R > 0,
          trade) %>% 
   mutate(trade = ifelse(trade, "Trading", "No Trading"),
          alpha = as.character(alpha)) %>% 
   group_by(trade, alpha, R, theta) %>%
   summarize(rev = sum(rev_tot)) %>%
   ungroup() %>%
   mutate(cost = (best_rev - rev) / best_rev) %>%
   ggplot(aes(x = R, y = cost, color = theta, group = paste(alpha, theta), linetype = alpha)) +
   geom_line(size = 1.5) +
   scale_y_continuous(labels = scales::percent,
                      limits = c(0, 1)) +
   scale_x_continuous(limits = c(0, 1)) +
   xlab("Portion of patch as reserve (R)") +
   ylab("Losses\n(relative to R = 0)") +
   scale_color_viridis_c() +
   scale_linetype_manual(values = c("solid", "dashed", "dotted")) +
   ggtheme_plot() +
   guides(color = guide_colorbar(title = bquote("Movement ("~theta~")"),
                                 ticks.colour = "black",
                                 frame.colour = "black"),
          linetype = guide_legend(title = bquote("Allocation ("~alpha~")"),
                                  override.aes = list(size = 0.5))))
```
